<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-10-29 MainAnalysis.Rmd
Switched to using DTXSIDs

Calculate a limit of quantification (90% of lowest observation)
```{r, calc_loq, eval = TRUE}
source.col <- "fk_study_id"
cas.col <- "dsstox_casrn"
media.col <- "conc_medium_normalized"
value.col <- "conc"
for (this.study in unique(cvt.data[,source.col]))
{
  this.subset1 <- subset(cvt.data,cvt.data[,source.col]==this.study)
  for (this.chem in unique(this.subset1[,cas.col]))
  {
    this.subset2 <- subset(this.subset1,this.subset1[,cas.col]==this.chem)
    for (this.media in unique(this.subset2[,media.col]))
    {
      this.subset3 <- subset(this.subset2,this.subset2[media.col]==this.media & 
        !is.na(this.subset2[,value.col]))
      this.subset3 <- subset(this.subset3,this.subset3[,value.col]>0)
      this.loq <- suppressWarnings(min(this.subset3[,value.col], na.rm=TRUE))
      this.loq <- this.loq*0.9
      cvt.data[
        cvt.data[,source.col]==this.study & 
        cvt.data[,cas.col]==this.chem & 
        cvt.data[,media.col]==this.media,"calc_loq"] <- this.loq
    }
  }
}
cvt.data <- subset(cvt.data,!is.infinite(calc_loq))

@@

```{r, run_invivoPKfit_1comp, eval = FALSE}
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

```{r, run_invivoPKfit_2comp, eval = TRUE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```
```{r, plot_2comp, eval=FALSE}
plot_conctime(PK.fit.table.2comp[[1]],cvt.data,"2compartment")
head(subset(PK.fit.table.2comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

```{r, run_invivoPKfit_flat, eval = TRUE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

>>>>

Calculate a limit of quantification (90% of lowest observation)
```{r, calc_loq, eval = TRUE}
cvt.data <- estimate_loq(cvt.data)
```

@@

```{r, run_invivoPKfit_1comp, eval = TRUE}
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
```

```{r, run_invivoPKfit_2comp, eval = TRUE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
    dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  suppress.messages=TRUE
))
```
```{r, plot_2comp, eval=FALSE}
plot_conctime(PK.fit.table.2comp[[1]],cvt.data,"2compartment")
head(subset(PK.fit.table.2comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

```{r, run_invivoPKfit_flat, eval = TRUE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
    dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  suppress.messages=TRUE
))
```
